Refugees in Toronto's Homeless Shelters: Evaluating the Impact of Recent Policies and Increased Funding

### 2024-01-25 outputs/paper/paper.qmd
Title Changed
Made the title more appropriate

---
title: "Refugees in Toronto's Homeless Shelters: Evaluating the Need and Impact of Recent Policies and Increased Funding"
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/Toronto-Refugee-Shelter.git"
date: 2024-01-25
date-format: long
abstract: "In July 2023, a policy was changed and funding was increased to combat the issue of refugees in Toronto facing homelessnes. An analysis of data from the past five years reveals that, despite a pre-existing upward trajectory in refugee figures prior to the July 2023, the subsequent influx of funding and policy adjustments led to increased refugee access. Further analysis can be performed once more data becomes available."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Refugees in Toronto's Homeless Shelters: Evaluating the Impact of Recent Policies and Increased Funding"
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/Toronto-Refugee-Shelter.git"
date: 2024-01-25
date-format: long
abstract: "In July 2023, a policy was changed and funding was increased to combat the issue of refugees in Toronto facing homelessnes. An analysis of data from the past five years reveals that, despite a pre-existing upward trajectory in refugee figures prior to the July 2023, the subsequent influx of funding and policy adjustments led to increased refugee access. Further analysis can be performed once more data becomes available."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
